VOCC outline

### 2020-04-19 ms/ms.Rmd
update panel plot sketch

To explore the potential for change in climate to predict local percent changes in biomass density, we used similar spatial GLMMs in order to control for spatial autocorrelation amongst cells. For each maturity class of each species the model estimates an independent random spatial field was and with and without either genus or family as possible phylogenetic grouping factors. .
For each species, only the fewest cells that encompass 95% of total mean biomass were included.
In all models mean biomass density was included as a covariate in order to reduce the influence of changes occurring only at either the highest or lowest densities for a particular species.
We attempt to predict change in biomass of each species as a function of local climate change (just temperature, just DO, or both temperature and DO) and an interaction between the mean climate of each cell and its local change estimate.
We model both biomass and climate as either velocities or as raw trends<!-- TODO: should (Fig. \@ref(fig:climate-maps)) be here?-->. In addition we attempt to assess the importance of the gradient component in velocity estimates by adding gradient to the model based on trends.
All covariates were scaled to their standard deviations.
Covariates capturing cell means were also centered <!-- If fishing included: (except fishing effort---so that estimates can be interpreted as in the absence of fishing)-->, but change variables were kept uncentred because an intercept of 0 change is more intuitive to interpret.
Models exploring change as simple trends use Gaussian distributions, while velocities are heavy-tailed and therefore modeled using a student-t (degrees of freedom fixed at 7). Trend models converged with 500 knots and both temperature and DO, while velocity models would only converge with one environment variable at a time and 200 knots. <!-- TODO: make sure knots are explained somewhere... -->
In addition to checking the spatial distribution of model residuals, we simulated fake biomass trends for each species (using variance and spatial correlation parameters unique to each species) and reran each model 3 times <!-- TODO: simulated null models 10 times? --> and compared the distribution of effect sizes and number of sig effects in our simulated null models with the actual estimates.

@@

```{r temp-chops, fig.cap="Maps of biotic (top) and temperature (bottom) trends underlying the interactions (middle) where y-axis is predicted biotic trend for a given standardized change in bottom temperature (y-axis) for each . ", out.width="10in"}
include_graphics(here("ms", "figs", "temp-chops.pdf"))
```

```{r do-chops, fig.cap="Dissolved oxygen ...", out.width="6in"}
include_graphics(here("ms", "figs", "do-chops.pdf"))
```

```{r coef-scatterplots, fig.cap="Main effect coefficients for relationship between biotic trends and changes in climate for species with different life history strategies. Mean age and depth are calculated across all sampled individuals of each maturity class (as defined by the length at 50 percent maturity threshold) within a species. Growth rate is estimated as the length at maturity for females divide by the 0.95 quantile of ages recorded for immatures of each species.", out.width="9in"}
include_graphics(here("ms", "figs", "coef-scatterplots.pdf"))
```

>>>>

To explore the potential for change in climate to predict local percent changes in biomass density, we used similar spatial GLMMs in order to control for spatial autocorrelation amongst cells. For each maturity class of each species the model estimates an independent random spatial field was and with and without either genus or family as possible phylogenetic grouping factors. .
For each species, only the fewest cells that encompass 95% of total mean biomass were included.
In all models mean biomass density was included as a covariate in order to reduce the influence of changes occurring only at either the highest or lowest densities for a particular species.
We attempt to predict change in biomass of each species as a function of local climate change (just temperature, just DO, or both temperature and DO) and an interaction between the mean climate of each cell and its local change estimate.
We model both biomass and climate as either velocities or as raw trends<!-- TODO: should (Fig. \@ref(fig:climate-maps)) be here?-->. In addition we attempt to assess the importance of the gradient component in velocity estimates by adding gradient to the model based on trends.
All covariates were scaled to their standard deviations.
Covariates capturing cell means were also centered <!-- If fishing included: (except fishing effort---so that estimates can be interpreted as in the absence of fishing)-->, but change variables were kept uncentred because an intercept of 0 change is more intuitive to interpret.
Models exploring change as simple trends use Gaussian distributions, while velocities are heavy-tailed and therefore modeled using a student-t (degrees of freedom fixed at 7). Trend models converged with 500 knots and both temperature and DO, while velocity models would only converge with one environment variable at a time and 200 knots. <!-- TODO: make sure knots are explained somewhere... -->
In addition to checking the spatial distribution of model residuals, we simulated fake biomass trends for each species (using variance and spatial correlation parameters unique to each species) and reran each model 3 times <!-- TODO: simulate null model 10 times? --> and compared the distribution of effect sizes and number of sig effects in our simulated null models with the actual estimates.

@@

```{r species-map-chop-panel, fig.cap="Maps of biotic (top), temperature (middle) and DO (bottom) trends underlying interaction plots (sandwiched between maps) of predicted biotic trend (y-xis) for each standard deviation in change in seafloor temperature and DO (x-axis) for sample species representing a range of taxonomic groups and response patterns.", out.width="9in"}
include_graphics(here("ms", "figs", "species-map-chop-panel.png"))
```

```{r coef-scatterplots, fig.cap="Main effect coefficients for relationship between biotic trends and changes in climate for species with different life history strategies. Mean age and depth are calculated across all sampled individuals of each maturity class (as defined by the length at 50 percent maturity threshold) within a species. Growth rate is estimated as the length at maturity for females divide by the 0.95 quantile of ages recorded for immatures of each species.", out.width="8in"}
include_graphics(here("ms", "figs", "coef-scatterplots.pdf"))
```
